Algebraic filtering of surfaces from medical images with Julia

### 2020-01-01 src/paper.tex
Updates from Overleaf

\begin{figure}
\centering
\includegraphics[width=0.3\textwidth]{figs/liver_01_red_3.png} 
\vspace{0.05\textwidth}
\includegraphics[width=0.3\textwidth]{figs/portalvein_01_yellow_3.png} 
\vspace{0.05\textwidth}
% \includegraphics[height=0.3\textwidth]{figs/nrn10_100_green.png} 
\includegraphics[height=0.3\textwidth]{figs/nrn10_100_low_res.png} 
%\includegraphics[scale=1]{input/ircad_comparison.pdf} 
\caption{
Triangulated isosurface of liver parts extracted with LAR-SURF algorithm. 
On the left image the surface of the liver parenchyma of human. 
The middle image shows the Portal Vein from the same Ircad dataset \cite{ircad} 
with resolution $1.6\times0.57\times0.57$ [mm].
On the right image is the pig liver microvasculature based on corrosion cast prepared by Eberlova
\cite{eberlova2017use}. The resolution of the Micro-CT data is 4.682 $\mu{}m$.
}
\label{fig:example_liver_macro_micro}
\end{figure}

The implementation of our algorithm is available in LarSurf package. 
Use of this package can be seen on listings \ref{lst:example1} where the liver segmentation with 2865131 voxels from
Ircad dataset is used as an input for our surface extraction algorithm. The size of 3D volumetric 
image is $129 \times 512 \times 512$
and the voxel resolution is $1.6\times0.57\times0.57$ [mm]. 
The output surface model created by  182124 triangles and the number of vertices is 90822. The visualization can 
be seen on left the image of figure \ref{fig:example_liver_macro_micro}. 
The portal vein surface extraction can be performed with a small change of input path in code.
It can be seen in the same image in the middle. The The 3D image resolution is the same. 
The number of input voxels is 103533. 
The output surface is created by 90822 vertices and 182124 triangles.

@@

\begin{figure}
\centering
\includegraphics[width=0.4\textwidth]{figs/porta_smoothing_1.png} 
\vspace{0.05\textwidth}
\includegraphics[width=0.4\textwidth]{figs/porta_smoothing_2.png} 
%\includegraphics[scale=1]{input/ircad_comparison.pdf} 
\caption{Triangulated isosurface of portal vein calculated with LAR-SURF}
\label{fig:example_porta}
\end{figure}

>>>>

% \includegraphics[height=0.3\textwidth]{figs/nrn10_100_green.png} 
%\includegraphics[scale=1]{input/ircad_comparison.pdf} 
\begin{figure}
\centering
\includegraphics[width=0.4\textwidth]{figs/liver_01_red_3.png} 
% \vspace{0.05\textwidth}
\includegraphics[width=0.4\textwidth]{figs/portalvein_01_yellow_3.png} 
% \vspace{0.01\textwidth}
\includegraphics[height=0.4\textwidth]{figs/nrn10_100_low_res.png} 
% \vspace{0.05\textwidth}
\includegraphics[width=0.4\textwidth]{figs/porta_smoothing_2.png} 
\caption{
Triangulated isosurface of liver parts extracted with LAR-SURF algorithm. 
On the upper left image the surface of the liver parenchyma of human can be seen. 
Both right images show the Portal Vein from the same Ircad dataset \cite{ircad} 
with resolution $1.6\times0.57\times0.57$ [mm].
On the left bottom image is the pig liver microvasculature based on corrosion cast prepared by Eberlova
\cite{eberlova2017use}. The resolution of the Micro-CT data is 4.682 $\mu{}m$.
} \label{fig:example_liver_macro_micro}
\end{figure}

% \begin{figure}
% \centering
% \includegraphics[width=0.4\textwidth]{figs/porta_smoothing_1.png} 
% \vspace{0.05\textwidth}
% \includegraphics[width=0.4\textwidth]{figs/porta_smoothing_2.png} 
% %\includegraphics[scale=1]{input/ircad_comparison.pdf} 
% \caption{Triangulated isosurface of portal vein calculated with LAR-SURF}
% \label{fig:example_porta}
% \end{figure}

The implementation of our algorithm is available in LarSurf package. 
Use of this package can be seen on listings \ref{lst:example1} where the liver segmentation with 2865131 voxels from
Ircad dataset is used as an input for our surface extraction algorithm. The size of 3D volumetric 
image is $129 \times 512 \times 512$
and the voxel resolution is $1.6\times0.57\times0.57$ [mm]. 
The output surface model created by  182124 triangles and the number of vertices is 90822. The visualization can 
be seen on figure \ref{fig:example_liver_macro_micro}. 
The portal vein surface extraction can be performed with a small change of input path in code.
The The 3D image resolution is the same. 
It can be seen in the same figure. 
The number of input voxels is 103533. 
The output surface is created by 90822 vertices and 182124 triangles.

@@
